---
title: "theCLE"
author: "Jessica Villa"
date: 'Summer 2022'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(lattice)
data("imagpop")
```

```{r}
KK_data <- imagpop$kkardashtemp
my1000 <- sample(KK_data, size = 1000, replace=T)
densityplot(my1000,main="original data")

```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

No it's not unimodal. It's bimodal. There are two peaks. Both peaks are the same size. There are 0 outliners in the plot. The mean is 49. The SD is 30.6. 

Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
```

For these data mean = 51.512, std = 26.8849898

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

No the plot isn't unimodal. The plot is trimodal. There is 3 peaks. The 3 peaks are not all the same. The peak in the middle is the largest peak and stands out the most. The two at the side are equal to each other. There are outliners. The mean is 50.3. The SD is 29.1. 

Do this again for 4 random samples

```{r}
numb = 4
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
```

There are 3 main peaks. There are 2 semi-forming peaksat the side. This plot is trimodal because there are 3 distinctive peaks. The main peak (in the middle) is larger than the rest. It reaches about .025. The two at the side are the same size and reach at about .0175. The mean is 50.3. The SD is 20.8. 

Then again for 9 random samples

```{r}
numb = 9
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
```

This is unimodal. Since there is 1 distinctive peak. It reaches about .029. There is 3 minor peaks. All 4 peaks have different values, none of them are the same size. The mean is 50.2. The SD is 13.5. 

then 16 random samples

```{r}
numb = 16
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
```

Only 1 peak so there can't be a comparison in size. The mean is 50.6. The SD is 10.6. 

finally for 36 random samples.

```{r}
numb = 36
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")
```

This plot is unimodal. There is only 1 peak so there can't be a comparison in peaks. The mean is 50. The SD is 6.7. 

Write a summary paragraph describing what you observed and how it relates to the central limit theorem.

Be sure to comment on both the mean and standard deviation of the sample averages - the CLT makes a statement about what to expect from both.

 

Then submit the link to your github project  to canvas to complete this assignment.